## Convert admin levels to Kobo XLSForms
### from hdx to choices in XLSForms 
### By Fuad Hudali , last updated 2017-07-07
### Modified on 2 July 2018
### Punya

### load libraries and generic functions
```{r}

suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(stringr))
suppressPackageStartupMessages(library(readxl))
suppressPackageStartupMessages(library(openxlsx))
suppressPackageStartupMessages(library(lubridate))


## clear all object from global environment
rm(list = ls())

## set governoarte pcodes to filter
#governorates_pcodes <- c("SY02", "SY07", "SY14")
# governorates_pcodes <- c("SY01", "SY03","SY05")  # Damascus rural damascus and hama
# governorates_pcodes <- c("SY02", "SY07")    ### Idleb and Aleppo

## load functions
#source("mygenericfunctions.R")
 # get timestamp for file names 
 tstamp <- format(Sys.time(),"_%Y%m%d_%H%M")

#Settings
 partner_code_name<-"Q_E6"
#
Sys.setlocale(category = "LC_ALL",locale = "arabic")
```

## Steps
1- download gazetteer from HDX
2- process it
3- export to excel




### download gazetteer from hdx and read the sheets

```{r}

#adminurl <- "https://data.humdata.org/dataset/356a63e9-90aa-4b9c-a938-58ef24469c00/resource/69663fc5-0aeb-4a4b-8cac-e58a4d2eb9a9/download/syr_admin_180627.xlsx"
#download.file(url=adminurl,destfile="syr_admin_180627.xlsx", mode='wb')
admin_xlsx<-"../Data/Admin/syr_admin_20180701.xlsx"
admin1 <- read_excel(admin_xlsx, sheet = "admin1",col_types = "text")
admin2 <- read_excel(admin_xlsx, sheet = "admin2", col_types = "text")
admin3 <- read_excel(admin_xlsx, sheet = "admin3", col_types = "text")
admin4 <- read_excel(admin_xlsx, sheet = "admin4", col_types = "text")
neighbourhood <- read_excel(admin_xlsx, sheet = "city_neighbourhoods", col_types = "text")
region <- read_excel("../kobo_users/regions.xlsx", sheet = "admin1_regions")
```

### read other datasets

```{r}
kobo_form <-"../xlsform/ochaMSNA2018v9_master.xlsx"

kobo_survey <- read_excel(kobo_form, sheet = "survey", col_types = "text")
kobo_choices <- read_excel(kobo_form, sheet = "choices",, col_types = "text")
kobo_settings <- read_excel(kobo_form, sheet = "settings",, col_types = "text")

turkey_coverage <-  read_excel("../kobo_users/MSNA2018_TurkeyXB_coverage_summary_govpcode.xlsx", sheet = "data")
nes_coverage <- read_excel("../kobo_users/MSNA2018_NES_coverage_summary_govpcode.xlsx", sheet = "data")
###
#syr_coverage <- read_excel("../kobo_users/Assessment_Locations_and_Kobo_Users_damascus.xlsx", sheet = "consolidated_list ")
#jor_coverage <- read_excel("../kobo_users/Assessment_Locations_and_Kobo_Users_jordan.xlsx", sheet = "consolidated_list ")

```



## process the admin levels to create them in choices format

```{r}

  filter_choices_18 <- function(keep_gov_s){
    #keep_gov_s <- c("SY02", "SY07")
  
  # admin1
    choices_admin1_s <- admin1 %>%  
                        filter(admin1Pcode %in% keep_gov_s) %>% 
                        select(admin1Name_ar,admin1Name_en,admin1Pcode) %>% 
                        mutate(listname = "govlist") %>% 
                        arrange(listname,admin1Name_ar)
  
  
    names(choices_admin1_s) <- c("label::Arabic (ar)","label::English (en)","name","list name")
  
  #label::Arabic	label::English	name	list name	govlist	distrlist	subdislist	comlist
  
  # admin2 
    admin2_ready_s <- admin2 %>% 
                      filter(admin1Pcode %in% keep_gov_s) %>% 
                      select(admin2Name_ar,admin2Name_en,admin2Pcode,admin1Pcode) %>% 
                      mutate(listname = "distlist", locationfilter = admin1Pcode) %>% 
                      select(-admin1Pcode) %>% 
                      arrange(listname,locationfilter,admin2Name_ar)
  
    names(admin2_ready_s) <- c("label::Arabic (ar)","label::English (en)","name","list name","locationfilter")
  
    choices_admin2_s <- choices_admin1_s %>% 
                        #mutate(admin1list = NA) %>% 
                        bind_rows(admin2_ready_s) # %>% 
  #arrange(`list name`,admin1list,`label::Arabic`)
  
  # admin3
   admin3_ready_s <- admin3 %>% 
                      filter(admin1Pcode %in% keep_gov_s) %>% 
                      select(admin3Name_ar,admin3Name_en,admin3Pcode,admin2Pcode) %>% 
                      mutate(listname = "sublist", admin2list = admin2Pcode ) %>% 
                      select(-admin2Pcode)%>% 
                      arrange(listname, admin2list,admin3Name_ar)
  
  names(admin3_ready_s) <- c("label::Arabic (ar)","label::English (en)","name","list name","locationfilter")
  
  choices_admin3_s <- choices_admin2_s %>% 
                      bind_rows(admin3_ready_s) # %>% 
  
  # choices_admin3 <- admin3_ready %>% bind_rows(choices_admin2) %>% 
  #                   arrange(`list name`,admin2list,`label::Arabic`)
  
  
  # admin4
  
  admin4_ready_s <- admin4 %>% 
                    filter(admin1Pcode %in% keep_gov_s) %>% 
                    select(admin4Name_ar,admin4Name_en,admin4Pcode,admin3Pcode) %>% 
                    mutate(listname = "comlist",admin3list = admin3Pcode) %>% 
                    select(-admin3Pcode) %>% 
                    arrange(listname, admin3list,admin4Name_ar)
  
  names(admin4_ready_s) <- c("label::Arabic (ar)","label::English (en)","name","list name","locationfilter")
  
  choices_admin4_s <- choices_admin3_s %>% 
                      bind_rows(admin4_ready_s) 
  
  # choices_admin4 <- admin4_ready %>% bind_rows(choices_admin3) %>% 
  #                   arrange(`list name`,admin3list,`label::Arabic`)
  # neighbourhoods
  neighbourhood_ready_s <- neighbourhood %>% 
                           filter(admin1Pcode %in% keep_gov_s) %>%  
                          select(neibourhoodName_ar,neibourhoodName_en,neibourhoodPcode,admin4Pcode) %>% 
                          mutate(listname = "nlist",admin4list = admin4Pcode) %>% 
                          select(-admin4Pcode) %>% 
                          arrange(listname, admin4list,neibourhoodName_ar)
  
 names(neighbourhood_ready_s) <- c("label::Arabic (ar)","label::English (en)","name","list name","locationfilter")
  
 if (nrow(neighbourhood_ready_s)==0){
     df_t<-data.frame(name=character(1))
     df_t$name<-"Cdummy"
     neighbourhood_ready_s<-bind_rows(neighbourhood_ready_s,df_t)
     neighbourhood_ready_s$`list name`<-"nlist"
 } 
 
 # choices_neighbourhood <- neighbourhood_ready %>% bind_rows(choices_admin4) %>% 
  #                   arrange(`list name`,admin4list,`label::Arabic`)
  
  choices_neighbourhood_s <- choices_admin4_s %>% 
                             bind_rows(neighbourhood_ready_s) %>% 
                             select(`list name`,name,`label::English (en)`,`label::Arabic (ar)`,locationfilter) 
  
  return(choices_neighbourhood_s)
}


## create the file


#fs <- filter_choices_18(governorates_pcodes)
#writexlsx(fs,paste("kobo_admin_choices",paste(governorates_pcodes, sep = "_", collapse = "_"),tstamp,".xlsx", sep = "_"))



```


## prepare common sheets - choices sheet


```{r}

## remove English from choices and rename arabic
kobo_choices_no_english <- kobo_choices %>% 
                           #rename(label=`label::Arabic (ar)` ) %>% 
                           drop_na(`list name`) %>%
                           select(-contains("::English"))
                           #select(`list name`,name,label,locationfilter,me) 
        

kobo_choices_no_admin <- kobo_choices_no_english %>%
                         filter(!(`list name` %in% c("govlist","distlist","sublist","comlist","nlist")))   ## remove admin1 to 4


## remove English from survey and rename arabic
kobo_survey_no_english <- kobo_survey %>% 
                          select(-contains("::English")) #%>% 
                          #rename(label = `label::Arabic (ar)`, hint = `hint::Arabic (ar)`, constraint_message = `constraint_message::Arabic (ar)`)

## rename settings sheet
kobo_settings_no_english <- kobo_settings #%>% 
                            #select(-default_language) 
  

### create regions admin data sets
regions_pcodes <- region %>%  
                  group_by(region) %>%
                  mutate(members = paste0(admin1Pcode, collapse = ",")) %>% 
                  select(region,members) %>% 
                  ungroup() %>% 
                  distinct(region,members) 
regions_pcodes

# generate region one : Centre

## get pcodes for the governoartes in Centre
reg1_pcodes <- regions_pcodes %>% 
               filter(region == "Centre") %>% 
               select(members)
#
g1 <- filter_choices_18(unlist(strsplit(reg1_pcodes$members, ","))) %>% 
      select(-contains("::English"))
      #rename(label=`label::Arabic` ) %>% 
      #select(`list name`, name, label, locationfilter)

## update survey sheet for centre
kobo_choices_centre <- kobo_choices_no_admin %>% 
                       bind_rows(g1) 
                      

## get pcodes for the governoartes in NW
reg2_pcodes <- regions_pcodes %>% filter(region == "NW") %>% select(members)

# 
g2 <- filter_choices_18(unlist(strsplit(reg2_pcodes$members, ","))) %>% 
      select(-contains("::English"))    
      #rename(label=`label::Arabic` ) %>% 
      #select(`list name`, name, label, locationfilter)
  
## update survey sheet for NW
kobo_choices_NW <- kobo_choices_no_admin %>%
                   bind_rows(g2) 

## get pcodes for the governoartes in NE
reg3_pcodes <- regions_pcodes %>% filter(region == "NES") %>% select(members)
# 
g3 <- filter_choices_18(unlist(strsplit(reg3_pcodes$members, ","))) %>% 
      select(-contains("::English"))    
  #rename(label=`label::Arabic` ) %>% 
      #select(`list name`, name, label, locationfilter)
  
## update survey sheet for NE
kobo_choices_NE <- kobo_choices_no_admin %>% bind_rows(g3)
## get pcodes for the governoartes in South
reg4_pcodes <- regions_pcodes %>% filter(region == "South") %>% select(members)
# 
g4 <- filter_choices_18(unlist(strsplit(reg4_pcodes$members, ","))) %>% 
      select(-contains("::English"))    
  #rename(label=`label::Arabic` ) %>% 
      #select(`list name`,name,label, locationfilter)
  
## update survey sheet for South
kobo_choices_South <- kobo_choices_no_admin %>% bind_rows(g4) 


## get pcodes for the governoartes in the coast
reg5_pcodes <- regions_pcodes %>% filter(region == "Coastal") %>% select(members)

# 

g5 <- filter_choices_18(unlist(strsplit(reg5_pcodes$members, ","))) %>% 
      select(-contains("::English"))    
      #rename(label=`label::Arabic` ) %>% 
      #select(`list name`, name, label, locationfilter)
  
## update survey sheet for coast
kobo_choices_Coastal <- kobo_choices_no_admin %>% bind_rows(g5) 

## south and rural Damascus
g6 <- filter_choices_18(c("SY12","SY13","SY14","SY03"))%>% 
      select(-contains("::English"))
      #rename(label=`label::Arabic` ) %>% 
      #select(`list name`,name,label,locationfilter)

## update survey sheet for coast
kobo_choices_jor <- kobo_choices_no_admin %>% bind_rows(g6) 


## all governorates
gall <- filter_choices_18(c("SY01","SY02","SY03","SY04","SY05","SY06","SY07","SY08","SY09","SY10","SY11","SY12","SY13","SY14")) %>%                           
        select(-contains("::English"))
        #rename(label=`label::Arabic` ) %>%
        #select(`list name`,name,label,locationfilter)

kobo_choices_all <- kobo_choices_no_admin %>% bind_rows(gall) 


```


## functions to help
```{r}
## function to create xlsform files
createxlsx <- function(fname,survey_df, choices_df, settings_df){
    wb <- openxlsx::createWorkbook()
    addWorksheet(wb,"survey")
    addWorksheet(wb,"choices")
    addWorksheet(wb,"settings")
    writeData(wb,survey_df,sheet="survey")
    writeData(wb,choices_df,sheet="choices")
    writeData(wb,settings_df,sheet="settings")
    saveWorkbook(wb, file=fname, overwrite = TRUE)
}

survey_title_ar <- "تقييم الاحتياجات الانسانية"
## function to change settings sheet
update_settings <- function(partnercode,set_region_ar, set_region_en){
  new_setting <- kobo_settings_no_english %>% 
                  mutate(new_id = paste0("syria_msna2018_",partnercode,"_",set_region_en), 
                         new_title = paste0(survey_title_ar,"-",paste0(set_region_ar,"_",set_region_en),"_",partnercode)
                        ) %>% 
                  select(-starts_with("form")) %>% 
                  rename(form_title = new_title, form_id = new_id) %>% 
                  select(form_title,form_id,default_language,submission_url,version)
 return(new_setting)
}
```

### create xls file for hub partners - one per governorate - USE THIS ONE
```{r}
#hub_list<- c("turkey", "syria", "jordan","nes")
hub_list<- c("nes")
for (hub in hub_list){
  #
  print (hub)
  if(hub=="turkey"){
    ## process partner data to assign regions to partners
    coverage <- turkey_coverage
    ## for each organization create xls files based on regions they ar active in
    kobo_master_name <- "../xlsform/tur/kobo_msna2018"
  }
  #---------------
  if(hub=="syria"){
    ## process partner data to assign regions to partners
    coverage <- syr_coverage 
    ## for each organization create xls files based on regions they ar active in
    kobo_master_name <- "../xlsform/syr/kobo_msna2018"
  }
  #--------------
  if(hub=="jordan"){
    ## process partner data to assign regions to partners
    coverage <- jor_coverage 
    ## for each organization create xls files based on regions they ar active in
    kobo_master_name <- "../xlsform/jor/kobo_msna2018"
  }
  
  #--------------
  if(hub=="nes"){
    ## process partner data to assign regions to partners
    coverage <- nes_coverage 
    ## for each organization create xls files based on regions they ar active in
    kobo_master_name <- "../xlsform/nes/kobo_msna2018"
  }
# ####coverage governorate list
#   coverage_govlist<- coverage %>% 
#                      select(starts_with("SY")) %>% 
#                      names()
#   
  #--loop through coverage of each hub
  coverage[is.na(coverage)]<-0
  for (i in 1:nrow(coverage)){
        ## update partner code default in the survey form
          coverage_names<-names(coverage)
          org_code<-coverage$organization_code[i] 
          print (org_code)
          #Survey - in KoBo file
          ind_row <- which(kobo_survey_no_english$name==partner_code_name)
          kobo_survey_no_english_i<-kobo_survey_no_english
          kobo_survey_no_english_i$default[ind_row]=org_code
          #----------------------------------#
          n_govnames<-length(which(str_detect(coverage_names,"SY")))+2
          for (i_col in 3:n_govnames){
            i_gov_pcode<-coverage_names[i_col]
            i_val<-as.numeric(coverage[i,i_col])
            #get gov name
            i_gov<-admin1 %>% 
                   filter(admin1Pcode==i_gov_pcode)
            #
            i_gov_name_en<-i_gov$admin1Name_en 
            i_gov_name_ar<-i_gov$admin1Name_ar
            #repalce string
            i_gov_name_en<-i_gov_name_en %>% 
                           str_replace_all(" ","") %>% 
                           str_replace_all("-","") %>%
                           str_replace_all("'","") 
            i_gov_name_ar<-i_gov_name_ar %>% 
                           str_replace_all(" ","") %>% 
                           str_replace_all("-","") %>% 
                           str_replace_all("'","") 
              
            if (i_val>0){
              #
              print (paste0(org_code,"----",i_gov_pcode))
              xlsfilename<-paste0(kobo_master_name,"_",org_code,"_",i_gov_pcode,"_",i_gov_name_en,".xlsx")
              ##KoBo settings - change
              #kobo_settings_updated <- update_settings(org_code,i_gov_name_ar,i_gov_name_en)
              new_id<-paste0("syria_msna2018_",org_code,"_",i_gov_pcode)
              new_title = paste0(org_code,"_",i_gov_name_ar,"_",survey_title_ar,"_",i_gov_name_en)
              
              kobo_settings_updated <- kobo_settings_no_english %>% 
                                       mutate(form_id = new_id, form_title=new_title) #%>% 
                                       #select(-starts_with("form")) %>% 
                                       #rename(form_title = new_title, form_id = new_id) %>% 
                                       #select(form_title,form_id,default_language,submission_url,version)
              #prepare filtered location list
              kobo_choices_gov_pcode<- filter_choices_18(i_gov_pcode) %>% 
                                       select(-contains("::English"))
              #combine with other choices list
              kobo_choices_updated<- kobo_choices_no_admin %>% bind_rows(kobo_choices_gov_pcode) 
              
              #SAVE XLSX FORM
              ## save to excel
              createxlsx(xlsfilename,kobo_survey_no_english_i,kobo_choices_updated,kobo_settings_updated)
            }
          }#each column
      }#each organisation
  print (hub)
}#each hub

```

### create xls file for a partner combining governorates
```{r}
partner_list<- c("3106")
gov_list<-c("SY08","SY09","SY11")
kobo_master_name <- "../xlsform/nes/kobo_msna2018"
for (partner in partner_list){  #
      print (partner)
        ## update partner code default in the survey form
          org_code<-partner
          print (org_code)
          #Survey - in KoBo file
          ind_row <- which(kobo_survey_no_english$name==partner_code_name)
          kobo_survey_no_english_i<-kobo_survey_no_english
          kobo_survey_no_english_i$default[ind_row]=org_code
          #----------------------------------#
          xlsfilename <- paste0(kobo_master_name,"_",org_code,".xlsx")
              ##KoBo settings - change
              #kobo_settings_updated <- update_settings(org_code,i_gov_name_ar,i_gov_name_en)
          new_id<-paste0("syria_msna2018","_",org_code)
          new_title = paste0(org_code,"_",survey_title_ar)
              
          kobo_settings_updated <- kobo_settings_no_english %>% 
                                   mutate(form_id = new_id, form_title=new_title) 
              #prepare filtered location list
          kobo_choices_gov_pcode<- filter_choices_18(gov_list) %>% 
                                   select(-contains("::English"))
          #combine with other choices list
          kobo_choices_updated<- kobo_choices_no_admin %>% bind_rows(kobo_choices_gov_pcode) 
              
          #SAVE XLSX FORM
          ## save to excel
          createxlsx(xlsfilename,kobo_survey_no_english_i,kobo_choices_updated,kobo_settings_updated)
}#partner
```

### NOT used create xls file for hub partners
```{r}
# hub_list<- c("turkey", "syria", "jordan","nes")
# for (hub in hub_list){
#   #
#   if(hub=="turkey"){
#     ## process partner data to assign regions to partners
#     coverage <- turkey_coverage %>% 
#                 select(NW,NES,Centre,Coastal,South,organization_code) #%>% filter(organization_code != 1729)
#     ## for each organization create xls files based on regions they ar active in
#     kobo_master_name <- "./xlsx_form/tur/kobo_msna2018_"
#   }
#   #---------------
#   if(hub=="syria"){
#     ## process partner data to assign regions to partners
#     coverage <- syr_coverage %>% 
#                 select(NW,NES,Centre,Coastal,South,organization_code) #%>% filter(organization_code != 1729)
#     ## for each organization create xls files based on regions they ar active in
#     kobo_master_name <- "./xlsx_form/syr/kobo_msna2018_"
#   }
#   #--------------
#   if(hub=="jordan"){
#     ## process partner data to assign regions to partners
#     coverage <- jor_coverage %>% 
#                 select(NW,NES,Centre,Coastal,South,organization_code) #%>% filter(organization_code != 1729)
#     ## for each organization create xls files based on regions they ar active in
#     kobo_master_name <- "./xlsx_form/jor/kobo_msna2018_"
#   }
#   
#   #--------------
#   if(hub=="nes"){
#     ## process partner data to assign regions to partners
#     coverage <- nes_coverage %>% 
#                 select(NW,NES,Centre,Coastal,South,organization_code) #%>% filter(organization_code != 1729)
#     ## for each organization create xls files based on regions they ar active in
#     kobo_master_name <- "./xlsx_form/nes/kobo_msna2018_"
#   }
# 
#   #--loop through coverage of each hub
#   for (i in 1:nrow(coverage)){
#         ## update partner code default in the survey form
#           org_code<-coverage$organization_code[i] 
#           #
#           ind_row <- which(kobo_survey_no_english$name==partner_code_name)
#           kobo_survey_no_english_i<-kobo_survey_no_english
#           kobo_survey_no_english_i$default[ind_row]=org_code
#          
#         #if partner works in Centre then create an xls file in centre
#         if(coverage$Centre[i] == 1){
#           xlsfilename <- paste0(kobo_master_name,org_code,"_centre",".xlsx")
#           ## change settings
#           kobo_settings_updated <- update_settings(org_code,"محافظات الوسط","centre")
#           kobo_choices_updated<- kobo_choices_centre
#         }
#       
#         if(coverage$NW[i] == 1){
#           xlsfilename <- paste0(kobo_master_name,org_code,"_NW",".xlsx")
#           ## change settings
#           kobo_settings_updated <- update_settings(org_code,"المحافظات في الشمال الغربي","NW")
#           kobo_choices_updated<- kobo_choices_NW
#         }
#       
#         if(coverage$NES[i] == 1){
#           xlsfilename <- paste0(kobo_master_name,org_code,"_NES",".xlsx")
#           ## change settings
#           kobo_settings_updated <- update_settings(org_code,"المحافظات في الشمال الشرقي","NE")
#           kobo_choices_updated<- kobo_choices_NE
#         }
#       
#          if(coverage$South[i] == 1){
#           xlsfilename <- paste0(kobo_master_name,org_code,"_South",".xlsx")
#           ## change settings
#           kobo_settings_updated <- update_settings(org_code,"المحافظات الجنوبية","South")
#           kobo_choices_updated<- kobo_choices_South
#          }
#       
#           if( coverage$Coastal[i] == 1){
#           xlsfilename <- paste0(kobo_master_name,org_code,"_Coastal",".xlsx")
#           ## change settings
#           kobo_settings_updated <- update_settings(org_code,"محافظات الساحل","Coastal")
#           kobo_choices_updated<- kobo_choices_Coastal
#           
#           }
#           
#         #save file
#           ## save to excel
#           createxlsx(xlsfilename,kobo_survey_no_english_i,kobo_choices_updated,kobo_settings_updated)
#       }
# }

```

## prepare NPM
```{r}
npm_code <- 1729
kobo_npm_name <- "../xlsform/npm/kobo_msna2018_"

   ind_row <- which(kobo_survey_no_english$name==partner_code_name)
   kobo_survey_no_english_npm<-kobo_survey_no_english
   kobo_survey_no_english_npm$default[ind_row]=npm_code

for (i in 1:nrow(admin1)){
  #if partner works in Centre then create an xls file in centre
 
    xlsfilename <- paste0(kobo_npm_name,npm_code,"_",admin1$admin1RefName[i],".xlsx")
    ## change settings
    npm_settings <- update_settings(npm_code,admin1$admin1Name_ar[i],admin1$admin1RefName[i])
    ## get choices
    ch <- filter_choices_18(admin1$admin1Pcode[i]) %>% 
          select(-contains("::English"))
          #rename(label=`label::Arabic` ) %>% 
          #select(`list name`, name, label, locationFilter)

## update survey sheet for NW
    kobo_choices_npm <- kobo_choices_no_admin %>% bind_rows(ch) 
    ## save to excel
    createxlsx(xlsfilename,kobo_survey_no_english_npm,kobo_choices_npm,npm_settings)
}

```

## for Jordan hub
## Dara,Qneitr Sweida and Rural Damascus

```{r}
# jor <- jor_coverage %>%  select(NW:organization_code)
# ## for each organization create xls files based on regions they ar active in
# kobo_master_name <- "./xlsx_form/jor/kobo_msna2018"
# 
# for (i in 1:nrow(jor)){
#    if(jor$South[i] == 1) {
#     xlsfilename <- paste0(kobo_master_name,jor$organization_code[i],"_south_rd",".xlsx")
#     ## change settings
#     south_settings <- update_settings(jor$organization_code[i],"المحافظات الجنوبية","South")
#     ## update partner code default
#     
#     ind_row <- which(kobo_survey_no_english$name==partner_code_name)
#     kobo_survey_no_english_jor<-kobo_survey_no_english
#     kobo_survey_no_english_jor$default[ind_row]=jor_coverage$organization_code[i]
#     ## save to excel
#     createxlsx(xlsfilename,kobo_survey_no_english_jor,kobo_choices_jor,south_settings)
#    }
# }
```

## create a form with all admin lists - ARABIC ONLY
```{r}
xlsfilename_all <- "../xlsform/kobo_syr_msna_2019_all.xlsx"
# update setteing 
new_id<-paste0("syria_msna2018","_",survey_title_ar,"_","all")
new_title = paste0("syria_msna2018","_",survey_title_ar,"_","all")
              
kobo_settings_updated <- kobo_settings_no_english %>% 
                         mutate(form_id = new_id, form_title=new_title)
## save to Excel
createxlsx(xlsfilename_all,kobo_survey_no_english,kobo_choices_all,kobo_settings_updated)
```